Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
added more to the threats to validity

%\paragraph{External validity} 
 To tackle the concern that the results of this study might not generalize to 
 other instances outside of the studied cases, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis that comprises 1,359 popular projects, which help to 
 build the notion that since we are building our analysis on top of a vast 
 data set, the threat of this analysis 
 not generalizing to other projects is mitigated.
\todo{mention the threat of the collapsing of data as you were discussing over email.}

>>>>

%\paragraph{External validity} 
 To tackle the concern that the results of this study might not generalize to 
 other instances outside of the studied cases, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis that comprises 1,359 popular projects, which help to 
 build the notion that since we are building our analysis on top of a vast 
 data set, the threat of this analysis 
 not generalizing to other projects is mitigated.

 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.
